Painting with Triangles

### 2014-06-05 paper.tex
foo

% uncomment one the following two lines, first one showing pictures
\documentclass[review]{acmsiggraph}
%\documentclass[review,draft]{acmsiggraph}

@@

\author{Mark D. Benjamin\thanks{e-mail:mdbenjam@princeton.edu} \hspace{10 pt} Princeton Unviersity\\ Adam Finkelstein\thanks{e-mail:af@cs.princeton.edu} \hspace{10 pt} Princeton University\\ Stephen DiVerdi\thanks{e-mail:diverdi@google.com} \hspace{10 pt} Google}
\pdfauthor{Mark D. Benjamin, Adam Finkelstein, Stephen Diverdi}

>>>>

% uncomment one the following two lines, first one showing pictures
\documentclass[annual]{acmsiggraph}
%\documentclass[annual,draft]{acmsiggraph}

@@

\author{Mark D. Benjamin \\ Princeton University \and 
Stephen DiVerdi \\ Google \and 
Adam Finkelstein \\ Princeton University}

\pdfauthor{Mark D. Benjamin, Stephen DiVerdi, Adam Finkelstein}
